%!TEX root = ../dynamics.tex
\section{Discussion}
\label{sec:discuss}

The main findings of our analysis are as follows:
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item Tasks related to audio transcription have been gaining momentum in the last years and are today the most popular tasks on \amt{}.
	\item The popularity of Content Access HITs has decreased over time. Surveys are however becoming more popular over time especially in the US.
	\item While most HITs do not require country-specific workers, most of such HITs require US-based workers.
	\item HITs that are exclusively asking for workers based in India have strongly decreased over time.
	\item Surveys are the most popular type of HITs for US-based workers.
	\item The most frequent HIT reward value has increased over time, and reaches \$0.05 in 2014.
	\item New requesters constantly join \amt{}, making the total number of active requesters and the available reward increase over time.
	\item The average HIT batch size is constant over time; however, very large batches have recently started to appear on the platform.
	\item The throughput of HIT batches can best be predicted based on the number of HITs available in the batch (i.e., its size) and its freshness.
	\item New HITs attract new workers to the platform.
	\item New workers arriving to the platform complete both fresh and old HITs.
	\item There is a weekly seasonality effect in the amount of rewards assigned to workers and HITs available.
\end{itemize}


A possible explanation for this is the lack of bidding (or negotiation) mechanisms available to the workers; such mechanisms are not available on the current platform though they could help workers drive the prices up. 

It must be noted that some workers might not be actively completing HITs on the platform but rather looking for HITs to work on by reading Web forums where other workers shared HITs. In that sense, new HITs attract new workers to the platform. This supplements our finding from Section \ref{sec:throughput}, where we showed that $start\_time$ is an important feature contributing to the pace of a batch.


This periodicity can either be rooted in the routine of workers